Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/casestudy.tex
PLACES: proofread case study

For the sake of code reuse for demonstration purposes, \cite{NoughtsAndCrosses}
uses \textit{higher-order components} (HOC) to build the correct state
implementations depending on which player the user chooses to be.
We leverage the \textit{Redux} \cite{Redux} state management library to keep track of game
state, thus showing the flexibility of our library design in being
interoperable with other libraries and idiomatic JavaScript practices.
% REVIEW: tight-coupling?
Our approach encourages the separation of concerns between the 
communication logic and program logic -- the generated session runtime
keeps track of the state of the EFSM to ensure protocol conformance by 
construction, whilst \textit{Redux} solely manages our game state.

>>>>

For the sake of code reuse, \cite{NoughtsAndCrosses}
uses \textit{higher-order components} (HOC) to build the correct state
implementations depending on which player the user chooses to be.
We leverage the \textit{Redux} \cite{Redux} state management library to keep track of game
state, thus showing the flexibility of our library design in being
interoperable with other libraries and idiomatic JavaScript practices.
% REVIEW: tight-coupling?
Our approach encourages the separation of concerns between the 
communication logic and program logic -- the generated session runtime
keeps track of the state of the EFSM to ensure protocol conformance by 
construction, whilst \textit{Redux} solely manages our game state.
